---
title: "network_analysis"
author: "Simon Weigold"
date: "2023-06-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r setup, include=FALSE, eval = F}
library(here)
source(here::here("scripts", "preparation.R"))
```

# Exploratory Data Analysis
Frequency distribution of streams
```{r}
freq_streams <- global %>% 
  ggplot(aes(x = streams)) +
  geom_freqpoly(bins = length(streams), col = "royalblue4") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_continuous(labels = scales::comma) +
  theme(axis.text = element_text(color="black", size=12, family="serif"),
        axis.text.x = element_text(color="black", size=12, family="serif"),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        axis.line.x = element_line(linewidth=0.5, color="grey"),
        axis.line.y = element_line(linewidth=0.5, color="grey"),
        panel.grid = element_line(color = "honeydew2",
                                  size = 0.5,
                                  linetype = 1),
        panel.background = element_rect(fill="white"),
        plot.margin = margin(10,10,10,10),
        plot.title = element_text(color="black", size=16, family="serif"),
        plot.subtitle = element_text(color="grey26", size=14, family="serif"),
        legend.text = element_text(color="black", size=12, family="serif"),
        text = element_text(color="black", size=14, family="serif")
  )

ggsave(freq_streams,
       filename = "freq_streams.png",
       path = here::here("imgs"),
       device = "png",
       width = 6, height = 4, units = "in",
       dpi = 600
       )

freq_streams
```

Frequency Distribution of Popularity
```{r}
freq_popularity <- metrics %>% 
  ggplot(aes(x = popularity)) +
  geom_freqpoly(binwidth = length(popularity), col = "royalblue4", na.rm = T) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_continuous(labels = scales::comma) +
  theme(axis.text = element_text(color="black", size=12, family="serif"),
        axis.text.x = element_text(color="black", size=12, family="serif"),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        axis.line.x = element_line(linewidth=0.5, color="grey"),
        axis.line.y = element_line(linewidth=0.5, color="grey"),
        panel.grid = element_line(color = "honeydew2",
                                  size = 0.5,
                                  linetype = 1),
        panel.background = element_rect(fill="white"),
        plot.margin = margin(10,10,10,10),
        plot.title = element_text(color="black", size=16, family="serif"),
        plot.subtitle = element_text(color="grey26", size=14, family="serif"),
        legend.text = element_text(color="black", size=12, family="serif"),
        text = element_text(color="black", size=14, family="serif")
  )

ggsave(freq_popularity,
       filename = "freq_popularity.png",
       path = here::here("imgs"),
       device = "png",
       width = 6, height = 4, units = "in",
       dpi = 600
       )

freq_popularity
```

Network Statistics for Subgraphs etc.
```{r}
# create DF
subgraph_metrics <- data.frame(c(1:9))
# Name
subgraph_metrics$subgraph <- c("Full Network", "Largest Subgraph",
                               V(subgraphs[[1]])$genre_recoded[1],
                               V(subgraphs[[2]])$genre_recoded[2],
                               V(subgraphs[[3]])$genre_recoded[3],
                               V(subgraphs[[4]])$genre_recoded[4],
                               V(subgraphs[[5]])$genre_recoded[5],
                               V(subgraphs[[6]])$genre_recoded[6],
                               V(subgraphs[[7]])$genre_recoded[7])
# Size
subgraph_metrics$size <- c(gsize(graph_artists),
                           gsize(largest_subgraph),
                           gsize(subgraphs[[1]]),
                           gsize(subgraphs[[2]]),
                           gsize(subgraphs[[3]]),
                           gsize(subgraphs[[4]]),
                           gsize(subgraphs[[5]]),
                           gsize(subgraphs[[6]]),
                           gsize(subgraphs[[7]])
                           )
# Density
subgraph_metrics$density <- c(edge_density(graph_artists),
                              edge_density(largest_subgraph),
                              edge_density(subgraphs[[1]]),
                              edge_density(subgraphs[[2]]),
                              edge_density(subgraphs[[3]]),
                              edge_density(subgraphs[[4]]),
                              edge_density(subgraphs[[5]]),
                              edge_density(subgraphs[[6]]),
                              edge_density(subgraphs[[7]])
                              )
# Components
subgraph_metrics$components <- c(count_components(graph_artists),
                           count_components(largest_subgraph),
                           count_components(subgraphs[[1]]),
                           count_components(subgraphs[[2]]),
                           count_components(subgraphs[[3]]),
                           count_components(subgraphs[[4]]),
                           count_components(subgraphs[[5]]),
                           count_components(subgraphs[[6]]),
                           count_components(subgraphs[[7]])
                           )
# Diameter
subgraph_metrics$diameter <- c(diameter(graph_artists, directed = F),
                           diameter(largest_subgraph, directed = F),
                           diameter(subgraphs[[1]], directed = F),
                           diameter(subgraphs[[2]], directed = F),
                           diameter(subgraphs[[3]], directed = F),
                           diameter(subgraphs[[4]], directed = F),
                           diameter(subgraphs[[5]], directed = F),
                           diameter(subgraphs[[6]], directed = F),
                           diameter(subgraphs[[7]], directed = F)
                           )
# Clustering
subgraph_metrics$transitivity <- c(transitivity(graph_artists),
                           transitivity(largest_subgraph),
                           transitivity(subgraphs[[1]]),
                           transitivity(subgraphs[[2]]),
                           transitivity(subgraphs[[3]]),
                           transitivity(subgraphs[[4]]),
                           transitivity(subgraphs[[5]]),
                           transitivity(subgraphs[[6]]),
                           transitivity(subgraphs[[7]])
                           )
```

Most occuring artists and wordcloud
```{r}
dplyr::count(df, artist, sort = T) %>% head(25)

wordcloud_artists <- wordcloud2::wordcloud2(data = count(df, artist), size = 0.35, color = "random-dark")
wordcloud_artists
#saveWidget(wordcloud_artists, here::here("imgs", "wordcloud-artists.html"), selfcontained = F)
#webshot(here::here("imgs", "wordcloud-artists.html"), here::here("imgs", "wordcloud-artists.png"), delay = 20, vwidth = 960, vheight = 960)
```

Most occuring songs and wordcloud
```{r}
dplyr::count(df, title, sort = T) %>% head(25)

wordcloud_songs <- wordcloud2::wordcloud2(data = count(df, title), size = 1, color = "random-dark")
wordcloud_songs
#saveWidget(wordcloud_songs, here::here("imgs", "wordcloud-songs.html"), selfcontained = F)
#webshot(here::here("imgs", "wordcloud-songs.html"), here::here("imgs", "wordcloud-songs.png"), delay =5, vwidth = 480, vheight=480)
```

```{r}
dep_var = inner_join(dep_var, popularity, by = "artist")
dep_var = inner_join(dep_var, genres, by = "artist")
dep_var = dep_var %>% select(-genre3)
dep_var = dep_var[order(-dep_var[,'Freq']),]
dep_var %>% head(25)
```

```{r}
dep_var = dep_var[order(-dep_var[,'streams']),]
dep_var %>% head(25)
```

```{r}
cor(dep_var$Freq, dep_var$streams)
cor(dep_var$Freq, dep_var$popularity, use = "na.or.complete")
```

```{r}
dep_var = dep_var[order(-dep_var[,'output']),]
dep_var %>% head(25)
```

Distribution of Genres
```{r}
genre_freq <- as.data.frame(table(genres$Genre))
genre_freq[order(-genre_freq[,'Freq']),] %>% head(25)
```

Distribution of meta Genres
```{r}
genre_freq <- as.data.frame(table(genres$genre2))
genre_freq[order(-genre_freq[,'Freq']),] %>% head(25)
```

```{r}
# Create plot_data
plot_data <- metrics_minmax %>% 
  tidyr::pivot_longer(cols = -c(artist, Genre, genre2, genre3),
                      names_to = "key", values_to = "value")
# Visualise relation distribution between variables and quality
par(family = "serif")
plot_data %>% 
  ggplot2::ggplot(aes(x = value), na.rm = T) + 
  ggplot2::geom_density(alpha = 0.6) +
  ggplot2::facet_wrap(~ key, scales = "free")
# Visualise relation between variables and quality in boxplots
par(family = "serif")
plot_data %>%
  ggplot2::ggplot(aes(y = value), na.rm = T)+
  ggplot2::geom_boxplot(alpha =0.6)+
  ggplot2::facet_wrap(~key, scales ="free")+
  ggplot2::theme(axis.title.x =element_blank(),
                 axis.text.x =element_blank(),
                 axis.ticks.x =element_blank())
```

Exploratory network analysis \n
```{r}
gsize(largest_subgraph) #size
edge_density(largest_subgraph) #density
count_components(largest_subgraph) #components
diameter(largest_subgraph, directed = F) #diameter
transitivity(largest_subgraph) #clustering
```


# Hypothesis 1
## Centrality measures
As a first step, the centrality measures are calculated.
```{r}
# see preparation
```

## Diagnostics of regression model
```{r}
regression <- lm(popularity ~ degree + betweenness + eigenvector,
                 data = metrics_minmax, na.action = na.exclude)
```

Diagnostics
1. Linearity
```{r}
par(family = "serif")
avPlots(regression)
```
2. No multicollinearity
```{r}
par(family = "serif")
metrics_minmax %>%
  dplyr::select(c(popularity, degree, betweenness, eigenvector)) %>% 
  stats::cor(use = "na.or.complete") %>% 
  corrplot::corrplot.mixed(upper = "color",
                 lower = "number",
                 tl.pos = "lt",
                 tl.col = "black",
                 lower.col = "black",
                 number.cex = 1)

CT <- cbind(metrics_minmax$degree, metrics_minmax$betweenness, metrics_minmax$closeness, metrics_minmax$eigenvector)
rcorr(CT)

vif(regression)
```
3. Homoskedasticity of the residuals
```{r}
plot(regression, 1)

bptest(regression)
```
4. Normality of the residuals
```{r}
hist(regression$residuals, breaks= 30, freq = F,
     main = "Distribution of residuals",
     xlab = "Residuals")
curve(dnorm(x, mean(regression$residuals), sd(regression$residuals)), 
      col = "red",
      add = T)
plot(regression, 2)
```

5. No influential points
```{r}
plot(regression, 4)
```

